\begin{problem} Consider the measure space $(\cX, 2^{\cX},\delta_x)$ where $\delta_x$ is the delta measure at $x\in \cX$. Let $f:\cX\to \overline{\bbR}$ be a non-negative measurable function. Show that 
\begin{equation*}
    \int_{\cX} f \,\De \delta_x = f(x).
\end{equation*}  
\end{problem}

\begin{problem} Let $(\Omega,\cF,\mu)$ be a measure space, $A\in \cF$, and $f:\Omega\to \overline{\bbR}$ be a non-negative  function. We say that $f$ is measurable on $A$ if $f|_{A}$ is $\cF_A$-measurable (recall that $\cF_A = \{A\cap B:\,B\in \cF\}$). Show that $f \indE{A}$ is $\cF$ measurable and also 
\begin{equation*}
    \int_\Omega f  \indE{A} \,\De \mu = \int_A f \,\De \mu_A, 
\end{equation*}
where $\mu_A$ is the restriction of $\mu$ to $\cF_A$.
\end{problem}

\begin{problem}
    Let $(\Omega,\cF,\mu)$ be a measure space and $f:\Omega\to \overline{\bbR}$ be a non-negative measurable function
    \begin{itemize}
        \item Let $A,B\in \cF$ be such that $A\subseteq B$. Show that
        \begin{equation*}
            \int_{A} f\,\De \mu \leq  \int_{B} f\,\De \mu.
        \end{equation*}
        \item Let $A,B\in \cF$ be such that $A\cap B = \varnothing$. Show that 
        \begin{equation*}
            \int_{A\cup B} f\,\De \mu =  \int_{A} f\,\De \mu + \int_{B} f\,\De \mu.
        \end{equation*}
    \end{itemize}
\end{problem}

\begin{problem}
     Suppose that $(f_n)\subseteq L^+$, $f_n\to f$ pointwise and $\lim_{n\to\infty} \int f_n\, \De\mu =  \int f\, \De\mu <\infty$. Show, without the dominated convergence theorem, that 
     for all $A\in \cF$
     \begin{equation*}
         \lim_{n\to\infty} \int_A f_n\,\De \mu = \int_A f\,\De \mu.
     \end{equation*}  
     Show that the conclusion might fail if $ \int f\, \De\mu = \infty$.
\end{problem}

\begin{problem}
    Let $(\Omega,\cF,\mu)$ be a measure space and  $(\Omega,\overline{\cF},\overline{\mu})$ its completion. Suppose that $f$ is integrable with respect to $\mu$. Show that $f$ is integrable with respect to $\overline{\mu}$ and in particular 
    \begin{equation*}
        \int_{\Omega} f\,\De \mu =  \int_{\Omega} f\,\De \overline{\mu}.
    \end{equation*}
    (\emph{Hint: start with simple functions.})
\end{problem}

\begin{problem} Let $(\Omega,\cF,\mu)$ be a measure space and suppose that $(f_{n})$ is a sequence of measurable functions such that $f_1\geq f_2\geq\ldots \geq 0$. Show using the MCT that if $f :=\lim_{n\to\infty} f_n$ and $\int_{\Omega} f_1<\infty$, then
\begin{equation*}
    \lim_{n\to\infty} \int_\Omega f_n\,\De \mu =  \int_\Omega f\,\De \mu.
\end{equation*}
Show that if $\int_{\Omega} f_1\,\De \mu = \infty$ the above conclusion might not hold.    
\end{problem}

\begin{problem}
    Let $(\Omega,\cF,\mu)$ be a measure space and $f\in L^+$. Show that if $\int f\,\De \mu <\infty$, then
    \begin{equation*}
        \lim_{n\to\infty} \int_\Omega f \ind{f\geq n} \,\De \mu = 0. 
    \end{equation*}
\end{problem}

\begin{problem} Let $(\Omega,\cF,\mu)$ be a measure space and assume that $f:\Omega\to \overline{\bbR}$ is integrable with respect to $\mu$. Show that $|f|<\infty$ $\mu$-almost everywhere.
    
\end{problem}

\begin{problem} Suppose that $f$ is a Lebesgue-integrable function on $\bbR$. Show that for all $z\in \bbR$
    \begin{equation*}
        \int_\bbR f(x)\,\De \cL^1(x) = \int_\bbR f(x+z)\,\De \cL^1(x).
    \end{equation*}
Show that for all $\tau \neq 0$
\begin{equation*}
    \int_\bbR f\Big(\frac{x}{\tau}\Big)\,\De \cL^1(x) = |\tau| \int_\bbR f(x)\,\De \cL^1(x).
\end{equation*}
\end{problem}

\begin{problem}
    Assume Fatou's lemma and deduce the Monotone Convergence Theorem.
\end{problem}

\begin{problem} Let $(\Omega,\cF,\mu)$ be a measure space and assume that $f$ is integrable with respect to $\mu$ and $g$ is a measurable function such that $f = g$ $\mu$-almost everywhere. Show that $g$ is integrable with respect to $\mu$ and 
    \begin{equation*}
        \int_\Omega f\, \De \mu =  \int_\Omega g\, \De \mu.
    \end{equation*}
\end{problem}

\begin{problem}  Let $(\Omega,\cF,\mu)$ be a measure space and $f$ be integrable with respect to $\mu$. Show that the set $\{\omega\in \Omega :\, f(\omega) \neq 0 \}$ is a $\sigma$-finite set. 
\end{problem}

\begin{problem}
    Let $(\Omega,\cF,\mu)$ be a measure space and $f,g$ be integrable with respect to $\mu$. Then 
    \begin{equation*}
        \int_A f \,\De \mu = \int_A g \,\De \mu,\qquad \forall A\in\cF,
    \end{equation*}
    if and only if $f = g$ $\mu$-almost everywhere, and if and only if $\int_{\Omega}|f-g|\,\De \mu = 0$.
\end{problem}

\begin{problem}
    Let $(\Omega_1,\cF_1)$ and $(\Omega_2,\cF_2)$ be two measure spaces. Let $f:\Omega_1\times\Omega_2\to \overline{\bbR}$, $f\geq 0$ be a $\cF_1\otimes \cF_2$-measurable function. Show that for all $y\in \Omega_2$ the map $f_y : \Omega_1\to \overline{\bbR}$, defined by $f_y(x) = f(x,y)$ for all $x\in \Omega_1$, is $\cF_1$-measurable.

    \noindent (\emph{Hint:} use approximations with simple functions.)
\end{problem}

\begin{problem}
    Let $f$ be Lebesgue-integrable on the real line. Show that
    \begin{equation*}
        \lim_{n\to\infty} \frac{1}{2 n} \int_{[-n,n]} f \,\De\cL^1 = 0.
    \end{equation*}
    Show that the result need not be true if $f$ is not assumed to be integrable on $\bbR$.
\end{problem}

\begin{problem} Let $\mu$ be a measure on $(\bbR,\cB_\bbR)$ concentrated on $\bbZ$. This means that $\mu(B) = \mu(B\cap \bbZ)$ for all $B\in \cB_\bbR$, or equivalently 
$\mu = \sum_{n\in \bbZ}\mu_n \delta_n$, where $\mu_n$ are non-negative real numbers and $\delta_n$ is the Dirac measura at $n\in \bbZ$. Show that $\mu_n = \mu(\{n\})$ for all $n\in \bbZ$ and that  for all $f$ non-negative and measurable
\begin{equation*}
    \int_\bbR f\,\De \mu = \sum_{n\in \bbZ} \mu_n f(n).
\end{equation*}
\end{problem}

\begin{problem}Consider the functions
    \begin{equation*}
        f_1(x) = \begin{cases}
            +\infty, & \text{if } x=0,\\
            \log|x|, & \text{if } 0<|x|<1,\\
            0, & \text{if }|x|\geq 1,
        \end{cases}
        \qquad 
        f_2(x) = \begin{cases}
            \frac{1}{x^2-1}, & \text{if } |x|\neq 0,\\
            20, & \text{if } |x| = 0,\\
        \end{cases}
        \qquad f_3(x)\equiv 1.
    \end{equation*}
    Determine if these functions are integrable on $(\bbR,\cB_\bbR)$ in each of the following two cases, and if possible compute the value of the integral
    \begin{enumerate}[a)]
        \item $m =\cL^1$ is the Lebesgue measure,
        \item $m$ is defined by
        \begin{equation*}
            m(B) = \sum_{n\in \bbZ} \frac{1}{1+(n+1)^2} \delta_n(B)
        \end{equation*}
    \end{enumerate}
    for all $B\in \cB_\bbR$.
\end{problem}

\begin{problem} Let $f,g: [0,1]\to\bbR$ be two non-negative integrable functions. Show that $fg$ is not necessarily integrable.
\end{problem}

\begin{problem} Let $f$ be integrable on $(\bbR,\cB_\bbR)$ with respect to the Lebesgue measure. 
    \begin{enumerate}[a)]
        \item Show that for all $\epsilon>0$ there exists a simple function $g = \sum_{i=1}^k a_i \indE{A_i}$ with $A_1,\ldots, A_k$ bounded intervals, such that $\int_\bbR |f-g|\,\De \cL<\epsilon$.
        \item Show that all $\epsilon>0$ there exists a bounded continuous function $h$ such that $\int_\bbR |f-h|\,\De \cL<\epsilon$.
    \end{enumerate}
\end{problem}

\begin{problem} Determine the limits of 
    \begin{equation*}
        \int_0^n \Big(1-\frac{x}{n}\Big)^n e^{x/2}\,\De x,\quad\text{and}\quad \int_0^n \Big(1+\frac{x}{n}\Big)^n e^{-2x}\,\De x.
    \end{equation*}
\end{problem}

\begin{problem} Let $(\Omega,\cF,\mu)$ be a finite measure space. Let $(f_n)_n$ be a sequence of measurable functions such that $f_n\to f$ uniformly on $\Omega$. Show that if $f_n$ is integrable for all $n\in\bbN$ then $f$ is also integrable and
    \begin{equation*}
        \lim_{n\to\infty} \int_\Omega f_n \,\De \mu = \int_\Omega f \,\De \mu. 
    \end{equation*}
Recall that $f_n$ converges uniformly to $f$ on $\Omega$ if $\lim_{n\to\infty} \sup_{\omega\in \Omega} |f_n(\omega)-f(\omega)| = 0$.
Show that the result is in general false if $\mu(\Omega) = \infty$.
\end{problem}

\begin{problem}
    Let $f:\bbR\to \bbR$ be integrable with respect to the Lebesgue measure. Show that the map $x\mapsto \int_{[-\infty,x]} f\,\De \cL$ is continuous in $x\in \bbR$.
\end{problem}

% \begin{problem}
%     Let $f_n(x) = a e^{-n a x} - b e^{-b n x}$ with $0<a<b$. Show that
%     \begin{enumerate}
%         \item $\sum_{n=1}^\infty \int_0^\infty |f_n|\,\De \cL = \infty$,
%         \item $\sum_{n=1}^\infty \int_0^\infty f_n\,\De \cL = 0$,
%         \item $\sum_{n=1}^\infty \int_0^\infty f_n\,\De \cL$ is summable and $\int_0^\infty \sum_{n=1}^\infty f_n \,\De \cL = \log(b/a)$.
%     \end{enumerate}
% \end{problem}
