
\begin{problem}
    Show that there is no $\sigma$-algebra with an odd number of elements.
\end{problem}

\begin{problem}
Let $(\Omega,\cF)$ be a measurable space and $A,B\in \cF$. Show, starting from the definition of $\sigma$-algebra, that $A\cup B$, $A\cap B$, $A\setminus B$, and $A\Delta B$ all belong to $\cF$.
\end{problem}

\begin{problem}
    Let $(\Omega,\cF)$ be a measurable space and $A_1, A_2,\ldots$ be a sequence of sets in $\cF$. Define the following sets
    \begin{equation*}
        \limsup_{n\to\infty} A_n = \bigcap_{n\in \bbN} \bigcup_{m\geq n} A_m,\qquad \liminf_{n\to\infty} A_n = \bigcup_{n\in \bbN} \bigcap_{m\geq n} A_m.
    \end{equation*}
    Show that:
    \begin{itemize}
        \item $(\limsup_{n\to\infty} A_n)^c = \liminf_{n\to\infty} A_n^c$,
        \item $\liminf_{n\to\infty} A_n \in \cF$ and $\limsup_{n\to\infty} A_n \in \cF$,
        \item $\liminf_{n\to\infty} A_n \subseteq \limsup_{n\to\infty} A_n$.
        \item  $\liminf_{n\to\infty} A_n = \{\omega \in \Omega:\, \omega\in A_n\text{ for infinitely many $n$}\}$.
        \item $\limsup_{n\to\infty} A_n = \{\omega \in \Omega:\, \text{$\exists m\in \bbN$ such that $\omega\in A_n$ for all $n\geq m$}\}$.
    \end{itemize}
\end{problem}

\begin{problem}
    Let $\Omega$, $E$ be non-empty, $\cG$ a $\sigma$-algebra on $E$ and $f:\Omega\to E$. Show that 
    \begin{equation*}
        \cF = \{f^{-1}(B):\,B\in \cG\},
    \end{equation*}
    is a $\sigma$-algebra on $\Omega$.
\end{problem}

\begin{problem}
    Let $(\Omega,\cF)$ be a measurable space and $(A_n)_{n\in \bbN}$ a collection of sets in $\cF$. Show that:
    \begin{itemize}
        \item There are $(E_n)_{n\in \bbN}\subseteq \cF$ mutually disjoint such that $\cup_{n\in \bbN} A_n = \cup_{n\in \bbN} E_n$.
        \item There are $(F_n)_{n\in \bbN}\subseteq \cF$ such that $F_n\subseteq F_{n+1}$ for all $n\in \bbN$ amd $\cup_{n\in \bbN} A_n = \cup_{n\in \bbN} E_n$.
    \end{itemize} 
\end{problem}

\begin{problem}
    Let $\Omega$ be a non-empty set and $\cF$ a non-empty collection of subsets of $\Omega$ which is closed under taking complements and finite unions (such a collection is called an \emph{algebra}). Show that $\cF$ is a $\sigma$-algebra if and only if it is closed under countable increasing unions (i.e., if $\{A_n\}\subseteq \cF$ and $A_1\subseteq A_2\subseteq \ldots$, then $\cup_{n\in \bbN} A_n \in \cF$).
\end{problem}
        

\begin{problem}(Restriction of $\sigma$-algebra)
    Let $\cF$ be a $\sigma$-algebra of subsets of $\Omega$. Suppose that $A\subseteq \Omega$ is non-empty. Show that
    \begin{equation*}
        \cF_A = \{B\cap A:\, B\in \cF\}
    \end{equation*}
    is a $\sigma$-algebra on $A$.
\end{problem}

\begin{problem}(Extension of $\sigma$-algebra) Let $(\Omega,\cF)$ be a measurable space, and let $K$ be some non-empty set such that $\Omega\cap K = \varnothing$. Define $\overline{\Omega} = \Omega \cup K$ and $\overline{\cF} = \sigma(\cF\cup K)$ be a $\sigma$-algebra on $\overline{\Omega}$. Show that $\overline{\cF} = \{A\subseteq \overline{\Omega}:\, A\cap \Omega\in \cF\}$.
    
\end{problem}

\begin{problem} Let $\Omega$ be a infinite non-empty set. 
    \begin{itemize}
        \item Define the collection of sets $\cF = \{A\subseteq \Omega:\, \text{$A$ is countable or $\Omega\setminus A$ is countable}\}$. Is $\cF$ a $\sigma$-algebra? Prove or disprove.
        \item Define the collection of sets $\cF = \{A\subseteq \Omega:\, \text{$A$ is finite or $\Omega\setminus A$ is finite}\}$. Is $\cF$ a $\sigma$-algebra? Prove or disprove.
    \end{itemize}
\end{problem}

\begin{problem}
    Let $\cF$ and $\cG$ be $\sigma$-algebras on $\Omega$. Show that $\cF\cap\cG$ is a $\sigma$-algebra. Prove or disprove whether $\cF\cup \cG$ is in general a $\sigma$-algebra.
\end{problem}


\begin{problem} Let $\cF_n$, $n\in \bbN$ be $\sigma$-algebras on $\Omega$ such that $\cF_{n}\subseteq \cF_{n+1}$ for all $n\in \bbN$ (such a sequence $\{\cF_n\}$ is called a \emph{filtration}). 
    \begin{itemize}
        \item Show that $\bigcup_{n\in \bbN} \cF_n$ is an algebra.
        \item Is $\bigcup_{n\in \bbN} \cF_n$ a $\sigma$-algebra? Consider $\Omega=\bbN$ and $\cF_n = \sigma(\{A:\,A\subseteq \bbN \cap \{1,\ldots n\}\})$).
    \end{itemize}
\end{problem}

\begin{problem}
    Let $\cE\subseteq \cA$ be two collections of sets. Show that $\sigma(\cE) \subseteq\sigma(\cA)$. 
\end{problem}

\begin{problem}(Product sigma algebra) Let $\Omega_1$ and $\Omega_2$ be two non-empty sets, and let $\cF_1$ and $\cF_2$ be $\sigma$-algebras on $\Omega_1$ and $\Omega_2$ respectively.
Consider the \emph{product $\sigma$-algebra} on $\Omega_1\times \Omega_2$
\begin{equation*}
    \cF_1\otimes\cF_2 := \sigma(\{A_1\times A_2:\, A_1\in \cF_1, A_2\in \cF_2\}.
\end{equation*}
Suppose that $\cF_1$ is generated by $\cA_1$ and $\cF_2$ is generated by $\cA_2$. Show that  $ \cF_1\otimes\cF_2$ is generated by $A_1\times A_2$ with $A_1\in \cA_1$ and $A_2\in \cA_2$.
\end{problem}

\begin{problem}
    Show that the Borel $\sigma$-algebra on $\bbR$ is generated by each of the following:
    \begin{enumerate}[i.] 
        \item the open intervals: $\cA_1 = \{(a,b):\, a<b\}$,
        \item the closed intervals: $\cA_2 = \{[a,b]:\, a < b\}$,
        \item the half open intervals $\cA_3 = \{[a,b):\, a < b\}$ or $\cA_4 = \{(a,b]:\, a < b\}$,
        \item the open rays: $\cA_5 = \{(a,\infty):\, a\in \bbR\}$ or $\cA_6 = \{(-\infty,a):\, a\in \bbR\}$,
        \item the closed rays: $\cA_7 = \{[a,\infty):\, a\in \bbR\}$ or $\cA_8 = \{(-\infty,a]:\, a\in \bbR\}$.
    \end{enumerate}
\end{problem}

\begin{problem}
    Recall that $\overline{\bbR} = \bbR\cup\{\pm\infty\}$ is the extended real line. Also recall that 
    \begin{equation*}
        \cB_{\overline{\cB}} = \{A\subseteq \overline{\cB}:\, A\cap \bbR \in \cB_{\bbR}\}
    \end{equation*}
    is a $\sigma$-algebra on $\overline{\bbR}$. Show that $\cB_{\overline{\cB}}$ is generated by the family of closed rays $\cA= \{[-\infty,a]:\,a\in \bbR\}$.
\end{problem}

\begin{problem}
    Let $\cF$ be an infinite $\sigma$-algebra. 
    \begin{itemize}
        \item Show that $\cF$ contains an infinite sequence of disjoint sets.
        \item (*) Show that $\mathrm{Card}(\cF)\geq \mathrm{Card}([0,1])$. \\(\emph{Hint:} think about binary representation of numbers in $[0,1]$).
    \end{itemize}
\end{problem}

\begin{problem}
    Show that $\Lambda$ is a $\lambda$-system on $\Omega$ if and only if
    \begin{enumerate}[I.]
        \item $\Omega\in \Lambda$,
        \item if $A,B\in \Lambda$ and $A\subseteq B$, then $B\setminus A\in \Lambda$,
        \item if $A_1,A_2,\ldots$ is a sequence of subsets in $\Lambda$ such that $A_n \subseteq A_{n+1}$ for all $n\in \bbN$, then
        \begin{equation*}
            \bigcup_{n\in \bbN} A_n \in \Lambda.
        \end{equation*}
    \end{enumerate}
\end{problem}


\begin{problem}
    Let $\Lambda$ be a $\lambda$-system. Show that $\varnothing\in \Lambda$.
\end{problem}

\begin{problem}
    Let $\cA$ be both a $\lambda$-system and a $\pi$-system. Show that $\cA$ is a $\sigma$-algebra.
\end{problem}